---
title: "E18 mouse brain, 07 - figures"
author: 'K.Lebrigand, R.Waldmann'
date: 'Compiled: `r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    code_folding: none
    theme: journal
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  cache.lazy = FALSE,
  tidy = TRUE
)
```

# Loading data

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

setwd("/data/10x_data/10x_rainer/")
source("00.import.R")
library(DropletUtils)
library("reshape2")
library(gameofthrones)

s1141 <- readRDS("output/rna.labels.rds")
clusters <- c("radial glia","cycling radial glia","intermediate progenitor", "imature Glutamatergic", "mature Glutamatergic","imature GABAergic","mature GABAergic", "Cajal-Retzius")

DimPlot(object = s1141, reduction = "tsne", cols=cell_type_color, label = FALSE, pt.size = 2)
pdf("figures/fig.2d.pdf", width=8, height=6, useDingbats=FALSE)
DimPlot(object = s1141, reduction = "tsne", cols=cell_type_color, label = FALSE, pt.size = 2)
dev.off()

iso1141 <- readRDS("output/iso.labels.rds")
DimPlot(object = iso1141, reduction = "tsne", group.by="illumina.ident", cols=cell_type_color, label = FALSE, pt.size = 2)
pdf("figures/fig.2e.pdf", width=8, height=6, useDingbats=FALSE)
DimPlot(object = iso1141, reduction = "tsne", group.by="illumina.ident", cols=cell_type_color, label = FALSE, pt.size = 2)
dev.off()

```

# Total UMIs / Median UMIs / median Genes in RNA / ISOG / ISO assays

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

sum(s1141@meta.data$nCount_RNA)
sum(s1141@meta.data$nCount_ISOG)
sum(s1141@meta.data$nCount_ISOGRNA)
sum(s1141@meta.data$nCount_ISO)

median(s1141@meta.data$nCount_RNA)
median(s1141@meta.data$nCount_ISOG)
median(s1141@meta.data$nCount_ISOGRNA)
median(s1141@meta.data$nCount_ISO)

median(s1141@meta.data$nFeature_ISOG)
median(s1141@meta.data$nFeature_ISOGRNA)
median(s1141@meta.data$nFeature_RNA)
median(s1141@meta.data$nFeature_ISO)

```

# Percentage Illumina molecules / Genes profiled with Nanopore reads (1141 cells)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

s1141@meta.data$nUMIsProfiled <- s1141@meta.data$nCount_ISOG*100/s1141@meta.data$nCount_RNA
mean(s1141@meta.data$nUMIsProfiled)

s1141@meta.data$nFeaturesProfiled <- s1141@meta.data$nFeature_ISOGRNA*100/s1141@meta.data$nFeature_RNA
mean(s1141@meta.data$nFeaturesProfiled)

median(s1141@meta.data$nFeature_ISOGRNA)
median(s1141@meta.data$nCount_ISOG)

dim(s1141@assays$ISO@counts)
write.table(dat, file="test.csv", sep=",")

sum(s1141@meta.data$nCount_ISOG)

sum(s1141@meta.data$nCount_ISO)

median(s1141@meta.data$nCount_ISOG)
median(s1141@meta.data$nCount_ISO)

```

# Percentage Illumina molecules / Genes profiled with Nanopore reads (190 cells)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

sub190 <- subset(s1141, subset = sample=="s190")
mean(sub190@meta.data$nCount_ISO)
mean(sub190@meta.data$nFeature_ISOGRNA)

median(sub190@meta.data$nUMIsProfiled)
median(sub190@meta.data$nFeaturesProfiled)

```

# Percentage Illumina molecules / Genes profiled with Nanopore reads (951 cells)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

sub951 <- subset(s1141, subset = sample=="s951")
median(sub951@meta.data$nUMIsProfiled)
median(sub951@meta.data$nFeaturesProfiled)

```

# Correlation plots illumina/Nanopore (r²)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

#pdf("Correlation.plots.pdf", width=10, height=8, useDingbats=FALSE)

s1141@meta.data$index <- "1"
s1141@meta.data$index[which(s1141@meta.data$sample == "s951")] <- "2"

plot1 <- ggplot(data=s1141@meta.data, aes(x=nFeature_RNA,y=nFeature_ISOGRNA)) +  geom_point(shape = 21, colour = "black", fill = col[as.numeric(s1141@meta.data$index)]) +
      theme_bw() + theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
      ggtitle("Fig.2a - Genes (r=0.99, r2=0.99)") +
      geom_abline(slope=1, intercept=-15, linetype=3) +
      labs(x="Illumina",y="Nanopore")

x <- cor.test(s1141@meta.data$nCount_RNA, s1141@meta.data$nCount_ISOG, method="pearson")$estimate
x*x

plot2 <- ggplot(data=s1141@meta.data, aes(x=nCount_RNA,y=nCount_ISOG)) +  geom_point(shape = 21, colour = "black", fill = col[as.numeric(s1141@meta.data$index)]) +
      theme_bw() + theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
      ggtitle("Fig.2b - UMIs (r=0.99, r2=0.99)") +
      geom_abline(slope=1, intercept=-15, linetype=3) +
      labs(x="Illumina",y="Nanopore")

x <- cor.test(s1141@meta.data$nFeature_RNA, s1141@meta.data$nFeature_ISOGRNA, method="pearson")$estimate
x*x

#plot2 <- plot1 <- ggplot(data=s1141@meta.data, aes(nCount_RNA)) + 
#                geom_histogram(breaks=seq(0, 20000, by = 500),col="black",aes(fill=nGene), fill="lightsteelblue3") + 
#                scale_fill_gradient("Count", low = "green", high = "red") +
#                labs(title="Illumina nUMI") +
#                labs(x="nUMI", y="Cells")

#plot2 <- ggplot(data=s1141@meta.data, aes(nCount_ISOG)) + 
#                geom_histogram(breaks=seq(0, 20000, by = 500),col="black",aes(fill=nGene),fill="lightsteelblue3") + 
#                scale_fill_gradient("Count", low = "green", high = "red") +
#                labs(title="Nanopore nUMI") + 
#                labs(x="nUMI", y="Cells")

plot_grid(plot1, plot2)

pdf("figures/fig.2ab.pdf", width=8, height=6, useDingbats=FALSE)
plot_grid(plot1, plot2)
dev.off()

plot1 <- ggplot(data=s1141@meta.data, aes(nFeature_RNA)) + 
                geom_histogram(breaks=seq(0, 5000, by = 100),col="black",aes(fill=nGene),fill="lightsteelblue3") + 
                scale_fill_gradient("Count", low = "green", high = "red") +
                labs(title="Illumina nGene") + 
                labs(x="nGene", y="Cells")

plot2 <- ggplot(data=s1141@meta.data, aes(nFeature_ISOG)) + 
                geom_histogram(breaks=seq(0, 5000, by = 100),col="black",aes(fill=nGene),fill="lightsteelblue3") + 
                scale_fill_gradient("Count", low = "green", high = "red") +
                labs(title="Nanopore nGene") + 
                labs(x="nGene", y="Cells")

plot_grid(plot1, plot2)

#dev.off()

```

# Correlation Illumina / Nanopore (r)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

common.cells <- rownames(s1141@meta.data)
common.genes <- intersect(rownames(s1141@assays$RNA@data), rownames(s1141@assays$ISOG@data))

df <- data.frame()
for (i in (1:length(common.cells))){
  t <- data.frame(s1141@assays$RNA@data[common.genes,common.cells[i]], s1141@assays$ISOG@data[common.genes,common.cells[i]])
  colnames(t) <- c("illu","nano")
  df <- rbind(df, data.frame("Illu/ONT same cell",cor.test(t$illu, t$nano)$estimate))
}
colnames(df) <- c("type","cor")
rownames(df) <- c()

median(df$cor)
#ggplot(data=df, aes(cor)) + geom_histogram(breaks=seq(0.7, 1, by = 0.025),col="black")

df2 <- data.frame()
for (i in (1:length(common.cells))){
  #print (i)
  random <- sample(1:length(common.cells), 5, replace=T)
  
  for (j in (1:length(random))){
    if(i != random[j]){
      
      t <- data.frame(s1141@assays$RNA@data[common.genes,common.cells[random[j]]], s1141@assays$ISOG@data[common.genes,common.cells[i]])
      colnames(t) <- c("illu","nano")
      df2 <- rbind(df2, data.frame("Illu/ONT different cell",cor.test(t$illu, t$nano)$estimate))
    }
  }
}
colnames(df2) <- c("type","cor")
rownames(df2) <- c()

```
Nanopore/Illumina same cell
```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}
median(df$cor)

```
Nanopore/Illumina different cell
```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}
median(df2$cor)
```

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=12}

whole <- rbind(df,df2)
#pdf("/home/lebrigand/10x_rainer/figures/Correlation.plots.boxplots.pdf", width=10, height=8, useDingbats=FALSE)
ggplot(whole, aes(x=type, y=cor, fill=type)) +
  geom_boxplot()+
  ggtitle("Fig.2c (same r=0.90, different=0.54)") +
  theme_classic()

pdf("figures/fig.2c.pdf", width=10, height=8, useDingbats=FALSE)
ggplot(whole, aes(x=type, y=cor, fill=type)) +
  geom_boxplot()+
  ggtitle("Fig.2c (same cell r=0.90, different cell r=0.54)") +
  theme_classic()
dev.off()

```

# fig.3abc

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=14}

DefaultAssay(object = s1141) <- "ISO"
FeaturePlot(object = s1141, features = c("Clta..ENSMUST00000170241.7", "Clta..ENSMUST00000107849.9"), blend=TRUE, cols=c("green","red"), reduction="tsne", ncol=3)

pdf("figures/fig.3abc.pdf", width=24, height=6, useDingbats=FALSE)
FeaturePlot(object = s1141, features = c("Clta..ENSMUST00000170241.7", "Clta..ENSMUST00000107849.9"), blend=TRUE, cols=c("green","red"), reduction="tsne", ncol=3)
dev.off()

DefaultAssay(object = s1141) <- "RNA"
FeaturePlot(object = s1141, features = c("Clta"), cols=custom.pal, reduction="tsne")

#pdf("figures/sup.fig.7.pdf", width=6, height=6, useDingbats=FALSE)
#FeaturePlot(object = s1141, features = c("Clta"), cols=custom.pal, reduction="tsne")
#dev.off()

```

# sup.fig.7

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=14}

DefaultAssay(object = s1141) <- "ISO"
FeaturePlot(object = s1141, features = c("Myl6..ENSMUST00000218127.1","Myl6..ENSMUST00000164181.1"), blend=TRUE, cols=c("green","red"), reduction="tsne", ncol=3)

pdf("figures/sup.fig.7.pdf", width=24, height=6, useDingbats=FALSE)
FeaturePlot(object = s1141, features = c("Myl6..ENSMUST00000218127.1","Myl6..ENSMUST00000164181.1"), blend=TRUE, cols=c("green","red"), reduction="tsne", ncol=3)
DefaultAssay(object = s1141) <- "RNA"
FeaturePlot(object = s1141, features = c("Myl6"), cols=custom.pal, reduction="tsne", pt.size=2, min.cutoff = 0)
dev.off()

```

# sup.fig.6

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=24}

pdf("figures/sup.fig.6.pdf", width=36, height=8, useDingbats=FALSE)

DefaultAssay(object = s1141) <- "ISO"
general <- c('Myl6','Clta','Tecr','Pkm','Cdc42','Smarcb1','Rps24','Sh3glb1','Psap','Gnas')

lst <- c()
for (i in (1:length(general))){
  x <- rownames(s1141@assays$ISO@counts)[grep(paste("^",general[i],"\\.\\.",sep=""), rownames(s1141@assays$ISO@counts))]
  lst <- c(lst,x)
}

DotPlot(object = s1141, features = lst, scale.max = 100) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) # RotatedAxis

DefaultAssay(object = s1141) <- "RNA"
print(DotPlot(object = s1141, features = general, scale.max = 100, cols = c("lightgrey", "red")) + theme(axis.text.x = element_text(angle = 90, hjust = 1))) # 

pdf("figures/sup.fig.6.pdf", width=36, height=8, useDingbats=FALSE)
DefaultAssay(object = s1141) <- "ISO"
DotPlot(object = s1141, features = lst, scale.max = 100) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
DefaultAssay(object = s1141) <- "RNA"
print(DotPlot(object = s1141, features = general, scale.max = 100, cols = c("lightgrey", "red")) + theme(axis.text.x = element_text(angle = 45, hjust = 1))) # 
dev.off()

```

# sup.fig.7

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=24}

DefaultAssay(object = s1141) <- "ISO"

lst <- rev(c('Myl6..ENSMUST00000164181.1','Myl6..ENSMUST00000218127.1','Clta..ENSMUST00000107849.9','Clta..ENSMUST00000170241.7','Clta..ENSMUST00000107851.9','Tecr..ENSMUST00000165740.8','Tecr..ENSMUST00000019382.16','Pkm..ENSMUST00000034834.15','Pkm..ENSMUST00000163694.3','Cdc42..ENSMUST00000051477.12','Cdc42..ENSMUST00000030417.9','Smarcb1..ENSMUST00000121304.1','Smarcb1..ENSMUST00000000925.9','Rps24..ENSMUST00000223999.1','Rps24..ENSMUST00000169826.2','Sh3glb1..ENSMUST00000198254.4','Sh3glb1..ENSMUST00000163279.5','Psap..ENSMUST00000179238.7','Psap..ENSMUST00000105465.7','Gnas..ENSMUST00000109087.7','Gnas..ENSMUST00000109084.7','Gnas..ENSMUST00000109083.1','Zfand6..ENSMUST00000178385.8','Zfand6..ENSMUST00000209117.1','Zcrb1..ENSMUST00000076070.8','Zcrb1..ENSMUST00000162160.7','Vps29..ENSMUST00000155671.7','Vps29..ENSMUST00000118830.7','Faim..ENSMUST00000112911.8','Faim..ENSMUST00000035038.7','Gas5..ENSMUST00000159706.7','Gas5..ENSMUST00000162558.7'))

DotPlot(object = s1141, features = lst, scale.max = 100) + theme(axis.text.x = element_text(angle = 45, hjust = 1))

general <- rev(c('Myl6','Clta','Tecr','Pkm','Cdc42','Smarcb1','Rps24','Sh3glb1','Psap','Gnas','Zfand6','Zcrb1','Vps29','Faim','Gas5'))

DefaultAssay(object = s1141) <- "RNA"
print(DotPlot(object = s1141, features = general, scale.max = 100, cols = c("lightgrey", "red")) + theme(axis.text.x = element_text(angle = 90, hjust = 1))) # 

pdf("figures/sup.fig.7.isoforms.pdf", width=12, height=6, useDingbats=FALSE)
DefaultAssay(object = s1141) <- "ISO"
DotPlot(object = s1141, features = lst, scale.max = 100) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
dev.off()

pdf("figures/sup.fig.7.genes.pdf", width=12, height=6, useDingbats=FALSE)
DefaultAssay(object = s1141) <- "RNA"
print(DotPlot(object = s1141, features = general, scale.max = 100, cols = c("lightgrey", "red")) + theme(axis.text.x = element_text(angle = 90, hjust = 1))) # 
dev.off()

```

# Clta barplot

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

DefaultAssay(object = s1141) <- "ISO"
isoforms <- rownames(s1141@assays$ISO@counts)[grep(paste("^Clta\\.\\.",sep=""), rownames(s1141@assays$ISO@counts))]
clusters <- unique(s1141@active.ident)
df <- data.frame()
for(i in 1:length(clusters)){
  #for(j in 1:length(isoforms)){
    y <- Matrix::rowSums(s1141@assays$ISO@counts[isoforms, WhichCells(s1141, ident=clusters[i])])
    df<-rbind(df,y)
  #}
}

colnames(df) <- str_replace(isoforms, "Clta\\.\\.", "")
rownames(df) <- clusters
freq_table <- prop.table(as.matrix(df), 1)*100

tmp <- melt(freq_table)
names(tmp) <- c("clusters", "isoforms", "percentage")


#Clta-202	ENSMUST00000107846.9	1710	218aa	
#Clta-205	ENSMUST00000107851.9	1135	248aa	
#Clta-203	ENSMUST00000107847.9	1121	230aa	
#Clta-204	ENSMUST00000107849.9	1099	236aa	
#Clta-206	ENSMUST00000170241.7	1079	218aa	
#Clta-201	ENSMUST00000107845.3	

corresp <- c("ENSMUST00000107851.9"="Clta-205","ENSMUST00000107845.3"="Clta-201","ENSMUST00000170241.7"="Clta-206","ENSMUST00000107849.9"="Clta-204","ENSMUST00000107847.9"="Clta-203")

tmp$ensembl <- corresp[tmp$isoforms]

ggplot(tmp, aes(x=clusters, y=percentage, fill=ensembl)) + 
      geom_bar(stat="identity") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
      scale_x_discrete(limits=c("radial glia", "cycling radial glia", "intermediate progenitor", "imature GABAergic", "mature GABAergic", "imature Glutamatergic", "mature Glutamatergic","Cajal-Retzius")) + 
      scale_fill_got(discrete = TRUE, option = "Stark") + 
      ggtitle("Clta isoforms expression")

pdf("figures/barplot.clta.pdf", width=8, height=6, useDingbats=FALSE)
ggplot(tmp, aes(x=clusters, y=percentage, fill=ensembl)) + 
      geom_bar(stat="identity") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
      scale_x_discrete(limits=c("radial glia", "cycling radial glia", "intermediate progenitor", "imature GABAergic", "mature GABAergic", "imature Glutamatergic", "mature Glutamatergic","Cajal-Retzius")) + 
      scale_fill_got(discrete = TRUE, option = "Stark") + 
      ggtitle("Clta isoforms expression")
dev.off()

```

# Myl6 barplot

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

DefaultAssay(object = s1141) <- "ISO"
isoforms <- rownames(s1141@assays$ISO@counts)[grep(paste("^Myl6\\.\\.",sep=""), rownames(s1141@assays$ISO@counts))]
clusters <- unique(s1141@active.ident)
df <- data.frame()
for(i in 1:length(clusters)){
  #for(j in 1:length(isoforms)){
    y <- Matrix::rowSums(s1141@assays$ISO@counts[isoforms, WhichCells(s1141, ident=clusters[i])])
    df<-rbind(df,y)
  #}
}

colnames(df) <- str_replace(isoforms, "Myl6\\.\\.", "")
rownames(df) <- clusters

df <- df[,c("ENSMUST00000218127.1","ENSMUST00000164181.1","ENSMUST00000219554.1")]

freq_table <- prop.table(as.matrix(df), 1)*100

tmp <- melt(freq_table)
names(tmp) <- c("clusters", "isoforms", "percentage")

corresp <- c("ENSMUST00000218127.1"="Myl6-206","ENSMUST00000164181.1"="Myl6-201","ENSMUST00000219554.1"="Myl6-212")

#Myl6-201	ENSMUST00000164181.1	665	151aa	
#Myl6-202	ENSMUST00000217733.1	1668	152aa	
#Myl6-211	ENSMUST00000219236.1	692	158aa	
#Myl6-206	ENSMUST00000218127.1	691	151aa	
#Myl6-205	ENSMUST00000217969.1	608	139aa	
#Myl6-203	ENSMUST00000217776.1	562	158aa	
#Myl6-215	ENSMUST00000220427.1	746	38aa	
#Myl6-214	ENSMUST00000220307.1	496	46aa	
#Myl6-213	ENSMUST00000219655.1	651	No protein
#Myl6-210	ENSMUST00000219100.1	620	No protein
#Myl6-208	ENSMUST00000218713.1	369	No protein	
#Myl6-209	ENSMUST00000218813.1	3040	No protein
#Myl6-207	ENSMUST00000218170.1	824	No protein	
#Myl6-212	ENSMUST00000219554.1	790	No protein	
#Myl6-204	ENSMUST00000217913.1	436	

tmp$ensembl <- corresp[tmp$isoforms]

ggplot(tmp, aes(x=clusters, y=percentage, fill=ensembl)) + 
      geom_bar(stat="identity") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
      scale_x_discrete(limits=c("radial glia", "cycling radial glia", "intermediate progenitor", "imature GABAergic", "mature GABAergic", "imature Glutamatergic", "mature Glutamatergic","Cajal-Retzius")) + 
      scale_fill_got(discrete = TRUE, option = "Stark") + 
      ggtitle("Myl6 isoforms expression")

pdf("figures/barplot.myl6.filter.pdf", width=8, height=6, useDingbats=FALSE)
ggplot(tmp, aes(x=clusters, y=percentage, fill=ensembl)) + 
      geom_bar(stat="identity") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
      scale_x_discrete(limits=c("radial glia", "cycling radial glia", "intermediate progenitor", "imature GABAergic", "mature GABAergic", "imature Glutamatergic", "mature Glutamatergic","Cajal-Retzius")) + 
      scale_fill_got(discrete = TRUE, option = "Stark") + 
      ggtitle("Myl6 isoforms expression")
dev.off()


```

# Myl6 barplot (filtered)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

# filter

DefaultAssay(object = s1141) <- "ISO"

#Myl6-201	ENSMUST00000164181.1	665	151aa	
#Myl6-206	ENSMUST00000218127.1	691	151aa	
#Myl6-214	ENSMUST00000220307.1	496	46aa	
#Myl6-212	ENSMUST00000219554.1	790	No protein	

isoforms <- c("Myl6..ENSMUST00000164181.1","Myl6..ENSMUST00000218127.1","Myl6..ENSMUST00000219554.1","Myl6..ENSMUST00000220307.1")
  
clusters <- unique(s1141@active.ident)
df <- data.frame()
for(i in 1:length(clusters)){
  #for(j in 1:length(isoforms)){
    y <- Matrix::rowSums(s1141@assays$ISO@counts[isoforms, WhichCells(s1141, ident=clusters[i])])
    df<-rbind(df,y)
  #}
}

colnames(df) <- str_replace(isoforms, "Myl6\\.\\.", "")
rownames(df) <- clusters

freq_table <- prop.table(as.matrix(df), 1)*100

tmp <- melt(freq_table)
names(tmp) <- c("clusters", "isoforms", "percentage")

tmp$ensembl <- corresp[tmp$isoforms]

pdf("figures/barplot.myl6.pdf", width=8, height=6, useDingbats=FALSE)
ggplot(tmp, aes(x=clusters, y=percentage, fill=ensembl)) + 
      geom_bar(stat="identity") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
      scale_x_discrete(limits=c("radial glia", "cycling radial glia", "intermediate progenitor", "imature GABAergic", "mature GABAergic", "imature Glutamatergic", "mature Glutamatergic","Cajal-Retzius")) + 
      scale_fill_got(discrete = TRUE, option = "Stark") + 
      ggtitle("Myl6 isoforms expression")
dev.off()

```

# Consensus molecule accuracy

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

metrics <- read.delim("data/190c/nanopore/s190_molinfos.txt", stringsAsFactors = F)
metrics <- metrics[,-c(1:2)]
metrics <- metrics[which(metrics$nbReads<11),]

ggplot(metrics, aes(x=nbReads, y=pctId, group=nbReads)) +
  geom_boxplot(outlier.shape = NA, fill='#466cb9', color="black") +
  scale_y_continuous(limits = c(0.8, 1), breaks = seq(0.8, 1, by = 0.02)) + 
  labs(title="%age identity function of nbReads / UMI",y="mapping %age identity", x = "nbRreads per UMI") + 
  theme_minimal() + 
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7","8","9","10"), labels=c("1","2","3","4","5","6","7","8","9","10"),limits=c("1","2","3","4","5","6","7","8","9","10"))

pdf("figures/sup.fig.5c.pdf", width=8, height=6, useDingbats=FALSE)
ggplot(metrics, aes(x=nbReads, y=pctId, group=nbReads)) +
  geom_boxplot(outlier.shape = NA, fill='#466cb9', color="black") +
  scale_y_continuous(limits = c(0.8, 1), breaks = seq(0.8, 1, by = 0.02)) + 
  labs(title="%age identity function of nbReads / UMI",y="mapping %age identity", x = "nbRreads per UMI") + 
  theme_minimal() + 
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7","8","9","10"), labels=c("1","2","3","4","5","6","7","8","9","10"),limits=c("1","2","3","4","5","6","7","8","9","10"))
dev.off()

```

# Percentage assignation per genes (190 cells)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

metrics <- read.delim("data/951c/nanopore/s951_genemetrics.txt", stringsAsFactors = F)
metrics$def_ratio <- (metrics$nbIsoformSet * 100) / metrics$nbUmis
#metrics <- metrics[which(metrics$total > 10),]
metrics$M <- log((metrics$nbIsoformSet+0.1)/(metrics$nbIsoformNotSet+0.1),2)
metrics$average <- log(metrics$nbUmis,2)
rownames(metrics) <- metrics$geneId
metrics <- metrics[,-c(1)]
metrics$id <- rownames(metrics)

gg <- ggplot(data=metrics, aes(x=average,y=def_ratio)) +  geom_point(color="darkgrey") +
      theme_bw() + theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
      ggtitle(paste("Percentage isoform assignation", sep="")) +
      labs(x="log2(expression)",y="pct_def")

#gg +  geom_text_repel(data=subset(metrics, metrics$def_ratio > 50 & metrics$average > 14), aes(label=id), size=3) +
#      geom_point(data=subset(metrics, metrics$def_ratio > 50 & metrics$average > 14), col="red")

#t <- subset(metrics, metrics$def_ratio > 50 & metrics$average > 10)
#t$id
#write.table(metrics, file="metrics.csv", sep=",")

gg +  geom_text_repel(data=metrics["Gria2",], aes(label=id), size=4) +
      geom_point(data=metrics["Gria2",], col="red") + 
      geom_text_repel(data=metrics["Myl6",], aes(label=id), size=4) +
      geom_point(data=metrics["Myl6",], col="blue")+
      geom_text_repel(data=metrics["Clta",], aes(label=id), size=4) +
      geom_point(data=metrics["Clta",], col="blue")

```

# Correlation heatmap sup.fig.4

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=8}

table(s1141@meta.data$illumina.ident,s1141@meta.data$sample)

annotation <- data.frame(CellType = factor(c("radial glia","radial glia","cycling radial glia","cycling radial glia","intermediate progenitor","intermediate progenitor", "imature Glutamatergic","imature Glutamatergic", "mature Glutamatergic","mature Glutamatergic","imature GABAergic","imature GABAergic","mature GABAergic", "mature GABAergic", "Cajal-Retzius", "Cajal-Retzius"), levels = clusters), Replicate=factor(c("s190","s951","s190","s951","s190","s951","s190","s951","s190","s951","s190","s951","s190","s951","s190","s951"), levels = c("s190","s951")))
rownames(annotation) <- paste(annotation$Replicate,annotation$CellType,sep="_")

ann_colors <- list(CellType = c("radial glia"="#E54532","cycling radial glia"="#7A5388","intermediate progenitor"="#2A76BB","imature Glutamatergic"="#38AEEF","mature Glutamatergic"="#4CB57C","imature GABAergic"="#A5A739","mature GABAergic"="#EA766B","Cajal-Retzius"="#F0E816"))

clusters <- c("radial glia","cycling radial glia","intermediate progenitor", "imature Glutamatergic", "mature Glutamatergic","imature GABAergic","mature GABAergic", "Cajal-Retzius")

```

## Illumina gene-level downsampled to median (Nanopore isoform-level)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=8}

s1141 <- readRDS("output/rna.labels.rds")
DefaultAssay(object = s1141) <- "RNA"
dat <- downsampleMatrix(s1141@assays$RNA@counts, 0.5, bycol=TRUE)
s1141 <- SetAssayData(s1141, slot = "counts", dat, assay = "RNA")
s1141 <- NormalizeData(s1141, assay="RNA",normalization.method = "LogNormalize", scale.factor = 5000)

median(s1141@meta.data$nCount_RNA)

df <- data.frame()
df <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$RNA@data[,which(s1141@meta.data$illumina.ident == "radial glia" & s1141@meta.data$sample == "s190")])))
colnames(df) <- paste("s190_","radial glia",sep="")
y <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$RNA@data[,which(s1141@meta.data$illumina.ident == "radial glia" & s1141@meta.data$sample == "s951")])))
colnames(y) <- paste("s951_","radial glia",sep="")
df <- cbind(df, y)

for (i in (2:length(clusters))){
  x <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$RNA@data[,which(s1141@meta.data$illumina.ident == clusters[i] & s1141@meta.data$sample == "s190")])))
  colnames(x) <- paste("s190_",clusters[i],sep="")
  df <- cbind(df, x)
  y <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$RNA@data[,which(s1141@meta.data$illumina.ident == clusters[i] & s1141@meta.data$sample == "s951")])))
  colnames(y) <- paste("s951_",clusters[i],sep="")
  df <- cbind(df, y)
} 

cormat1<-signif(cor(df),2)

pheatmap::pheatmap(cormat1, cluster_rows = T, cluster_cols = T, 
                        annotation_col = annotation, annotation_colors = ann_colors,     
                        angle_col = 90, annotation_legend = F, clustering_method = "ward.D")

```

## Nanopore gene-level downsampled to median (Nanopore isoform-level)

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=8}

s1141 <- readRDS("output/rna.labels.rds")
DefaultAssay(object = s1141) <- "ISOG"
dat <- downsampleMatrix(s1141@assays$ISOG@counts, 0.62, bycol=TRUE)
s1141 <- SetAssayData(s1141, slot = "counts", dat, assay = "ISOG")
s1141 <- NormalizeData(s1141, assay="ISOG",normalization.method = "LogNormalize", scale.factor = 5000)

median(s1141@meta.data$nCount_ISOG)

df <- data.frame()
df <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISOG@data[,which(s1141@meta.data$illumina.ident == "radial glia" & s1141@meta.data$sample == "s190")])))
colnames(df) <- paste("s190_","radial glia",sep="")
y <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISOG@data[,which(s1141@meta.data$illumina.ident == "radial glia" & s1141@meta.data$sample == "s951")])))
colnames(y) <- paste("s951_","radial glia",sep="")
df <- cbind(df, y)

for (i in (2:length(clusters))){
  x <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISOG@data[,which(s1141@meta.data$illumina.ident == clusters[i] & s1141@meta.data$sample == "s190")])))
  colnames(x) <- paste("s190_",clusters[i],sep="")
  df <- cbind(df, x)
  y <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISOG@data[,which(s1141@meta.data$illumina.ident == clusters[i] & s1141@meta.data$sample == "s951")])))
  colnames(y) <- paste("s951_",clusters[i],sep="")
  df <- cbind(df, y)
} 

cormat2<-signif(cor(df),2)

pheatmap::pheatmap(cormat2, cluster_rows = T, cluster_cols = T, 
                        annotation_col = annotation, annotation_colors = ann_colors,     
                        angle_col = 90, annotation_legend = F, clustering_method = "ward.D")

```

## Nanopore isoform-level

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=6, fig.width=8}

s1141 <- readRDS("output/rna.labels.rds")
DefaultAssay(object = s1141) <- "ISO"
s1141 <- NormalizeData(s1141, assay="ISO",normalization.method = "LogNormalize", scale.factor = 5000)

mean(s1141@meta.data$nCount_ISO)
median(s1141@meta.data$nCount_ISO)

df <- data.frame()
df <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISO@data[,which(s1141@meta.data$illumina.ident == "radial glia" & s1141@meta.data$sample == "s190")])))
colnames(df) <- paste("s190_","radial glia",sep="")
y <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISO@data[,which(s1141@meta.data$illumina.ident == "radial glia" & s1141@meta.data$sample == "s951")])))
colnames(y) <- paste("s951_","radial glia",sep="")
df <- cbind(df, y)

for (i in (2:length(clusters))){
  x <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISO@data[,which(s1141@meta.data$illumina.ident == clusters[i] & s1141@meta.data$sample == "s190")])))
  colnames(x) <- paste("s190_",clusters[i],sep="")
  df <- cbind(df, x)
  y <- as.data.frame(Matrix::rowMeans(as.matrix(s1141@assays$ISO@data[,which(s1141@meta.data$illumina.ident == clusters[i] & s1141@meta.data$sample == "s951")])))
  colnames(y) <- paste("s951_",clusters[i],sep="")
  df <- cbind(df, y)
} 

cormat3<-signif(cor(df),5)

pheatmap::pheatmap(cormat3, cluster_rows = T, cluster_cols = T, 
                        annotation_col = annotation, annotation_colors = ann_colors,     
                        angle_col = 90, annotation_legend = F, clustering_method = "ward.D")

pdf("figures/sup.fig.4.pdf", width=8, height=6, useDingbats=FALSE)
print(pheatmap::pheatmap(cormat1, cluster_rows = T, cluster_cols = T, 
                        annotation_col = annotation, annotation_colors = ann_colors,     
                        angle_col = 90, annotation_legend = F, clustering_method = "ward.D"))
print(pheatmap::pheatmap(cormat2, cluster_rows = T, cluster_cols = T, 
                        annotation_col = annotation, annotation_colors = ann_colors,     
                        angle_col = 90, annotation_legend = F, clustering_method = "ward.D"))
print(pheatmap::pheatmap(cormat3, cluster_rows = T, cluster_cols = T, 
                        annotation_col = annotation, annotation_colors = ann_colors,     
                        angle_col = 90, annotation_legend = F, clustering_method = "ward.D"))
dev.off()

```

# CAGE peak / polyA site distribution

```{r message=FALSE, warning=FALSE, echo=FALSE, eval=T, fig.height=4, fig.width=6}

metrics <- read.delim("novel.txt", stringsAsFactors = F)

pdf("figures/polya.pdf", width=8, height=6, useDingbats=FALSE)
metrics %>% ggplot( aes(x=dist_polya)) +
    geom_histogram(breaks=seq(-50, 50, by = 1), color="black", fill="lightsteelblue3")+
    labs(title="Distance to polyA signal") + 
    labs(x="Distance to polyA signal", y="Number of Novel validated")
dev.off()

pdf("figures/cage.pdf", width=8, height=6, useDingbats=FALSE)
metrics %>% ggplot( aes(x=dist_cage)) +
    geom_histogram(breaks=seq(-50, 50, by = 1), color="black", fill="lightsteelblue3")+
    labs(title="Distance to CAGE peak") + 
    labs(x="Distance to CAGE peak", y="Number of Novel validated")
dev.off()

```

# Session Info

```{r sessinf}
sessionInfo()
```
